|

### 2023-04-05 paper.Rmd
Update Links/URLs.

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown^[Corresponding address: mail@paulcbauer.de. Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author:
  - Paul Bauer, Mannheim Centre for European Social Research
  - Camille Landesvatter, Mannheim Centre for European Social Research
date: |
  |       
  | First version: December 14, 2018
  | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
  | Download: https://osf.io/q395s
  |
  | Feedback? Errors? mail@paulcbauer.eu
  | [Github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)
  |
  | Tired of Latex?
  | Try [Pagedown](https://github.com/rstudio/pagedown) with our [new template](https://osf.io/k8jhx/)! :-)
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
---

@@

* ...install [R](https://www.r-project.org/) and [Rstudio](https://www.rstudio.com/) (most recent versions) [@R2017; @Rstudio2015].
* ...install [tinytex](https://yihui.name/tinytex/), a lightweight version of Tex Live [@markdown2017; @tinytex].
```{r eval=FALSE, include=TRUE}
install.packages(c('tinytex', 'rmarkdown'))
tinytex::install_tinytex()
```
* ...install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra; @plotly].
```{r eval=FALSE, include=TRUE}
install.packages(c("rmarkdown", "knitr", "kableExtra",
                   "stargazer", "plotly", "knitr",
                   "bookdown"))
```
* ...download the 5 input files we created --- `paper.rmd`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). Ignore the other files.

@@

[Download these files](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing) and save them into a folder. Close R/Rstudio and directly open `paper.rmd` with RStudio. Doing so assures that the working directory is set to the folder that contains `paper.rmd` and the other files.^[You can always check your working directory in R with `getwd()`.]

@@

In the present document we use the style of the American Sociological Association and set it in the preamble with `csl: american-sociological-association.csl`. However, you also need to download the respective `.csl` file from the following github page: https://github.com/citation-style-language/styles and copy it into your working directory for it to work.

The github directory contains a wide variety of citation style files depending on what discipline you work in.

>>>>

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown^[Corresponding address: mail@paulcbauer.de. Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author:
  - Paul Bauer, Mannheim Centre for European Social Research
  - Camille Landesvatter, Mannheim Centre for European Social Research
date: |
  |       
  | First version: December 14, 2018
  | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
  | Download: https://osf.io/q395s
  |
  | Feedback? Errors? mail@paulcbauer.de
  | [Github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)
  |
  | Tired of Latex?
  | Try [Pagedown](https://github.com/rstudio/pagedown) with our [new template](https://osf.io/k8jhx/)! :-)
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown) (click on Code -> Download ZIP). We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding [Github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
---

@@

* ...install [R](https://www.r-project.org/) and [Rstudio](https://www.rstudio.com/) (most recent versions) [@R2017; @Rstudio2015].
* ...install [tinytex](https://yihui.name/tinytex/), a lightweight version of Tex Live [@markdown2017; @tinytex].
```{r eval=FALSE, include=TRUE}
install.packages(c('tinytex', 'rmarkdown'))
tinytex::install_tinytex()
```
* ...install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra; @plotly].
```{r eval=FALSE, include=TRUE}
install.packages(c("rmarkdown", "knitr", "kableExtra",
                   "stargazer", "plotly", "knitr",
                   "bookdown"))
```
* ...download the 5 input files we created --- `paper.rmd`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [Github](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown) (click on Code -> Download ZIP). Ignore the other files.

@@

[Download these files from Github](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown) (click on Code -> Download ZIP) and save them into a folder. Close R/Rstudio and directly open `paper.rmd` with RStudio. Doing so assures that the working directory is set to the folder that contains `paper.rmd` and the other files.^[You can always check your working directory in R with `getwd()`.]

@@

In the present document we use the style of the American Sociological Association and set it in the preamble with `csl: american-sociological-association.csl`. However, you also need to download the respective `.csl` file from the following Github page: https://github.com/citation-style-language/styles and copy it into your working directory for it to work.

The Github directory contains a wide variety of citation style files depending on what discipline you work in.

### 2023-04-05 paper.tex
Update Links/URLs.

\title{\hfill\break
\hfill\break
\vspace{1cm}Writing a reproducible paper\\
in R Markdown\footnote{Corresponding address: \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}. Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
\author{Paul Bauer, Mannheim Centre for European Social Research \and Camille Landesvatter, Mannheim Centre for European Social Research}
\date{\hfill\break
First version: December 14, 2018\\
This version: March 08, 2023\\
Download: \url{https://osf.io/q395s}\\
\strut \\
Feedback? Errors? \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\
\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}\\
\strut \\
Tired of Latex?\\
Try \href{https://github.com/rstudio/pagedown}{Pagedown} with our \href{https://osf.io/k8jhx/}{new template}! :-)}

\begin{document}
\maketitle
\begin{abstract}
\noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below we outline some of the ``tricks''/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be downloaded \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{here}. We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{github repo}).\vspace{.8cm}
\end{abstract}

@@

\begin{itemize}
\item
  \ldots download the 5 input files we created --- \texttt{paper.rmd}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this folder}. Ignore the other files.
\item
  \ldots learn R and read about the other underlying components namely \href{https://en.wikipedia.org/wiki/Markdown}{Markdown}, \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
\end{itemize}

@@

\href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{Download these files} and save them into a folder. Close R/Rstudio and directly open \texttt{paper.rmd} with RStudio. Doing so assures that the working directory is set to the folder that contains \texttt{paper.rmd} and the other files.\footnote{You can always check your working directory in R with \texttt{getwd()}.}

@@

In the present document we use the style of the American Sociological Association and set it in the preamble with \texttt{csl:\ american-sociological-association.csl}. However, you also need to download the respective \texttt{.csl} file from the following github page: \url{https://github.com/citation-style-language/styles} and copy it into your working directory for it to work.

The github directory contains a wide variety of citation style files depending on what discipline you work in.

@@

\begin{verbatim}
## R version 4.2.2 (2022-10-31)
## Platform: aarch64-apple-darwin20 (64-bit)
## Running under: macOS Ventura 13.0.1
## 
## Matrix products: default
## BLAS:   /Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/lib/libRblas.0.dylib
## LAPACK: /Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/lib/libRlapack.dylib
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] ggplot2_3.3.6    kableExtra_1.3.4 knitr_1.39       stargazer_5.2.3 
## 
## loaded via a namespace (and not attached):
##  [1] compiler_4.2.2    pillar_1.7.0      tools_4.2.2       digest_0.6.29    
##  [5] evaluate_0.15     lifecycle_1.0.1   tibble_3.1.7      gtable_0.3.0     
##  [9] viridisLite_0.4.0 pkgconfig_2.0.3   rlang_1.0.6       DBI_1.1.2        
## [13] cli_3.3.0         rstudioapi_0.13   yaml_2.3.5        xfun_0.37        
## [17] fastmap_1.1.0     withr_2.5.0       dplyr_1.0.9       httr_1.4.3       
## [21] stringr_1.4.0     xml2_1.3.3        generics_0.1.2    vctrs_0.4.1      
## [25] systemfonts_1.0.4 tidyselect_1.1.2  webshot_0.5.3     grid_4.2.2       
## [29] svglite_2.1.0     glue_1.6.2        R6_2.5.1          fansi_1.0.3      
## [33] rmarkdown_2.20    bookdown_0.27     farver_2.1.0      purrr_0.3.4      
## [37] magrittr_2.0.3    scales_1.2.0      htmltools_0.5.2   ellipsis_0.3.2   
## [41] assertthat_0.2.1  rvest_1.0.2       colorspace_2.0-3  labeling_0.4.2   
## [45] utf8_1.2.2        stringi_1.7.6     munsell_0.5.0     crayon_1.5.1
\end{verbatim}

>>>>

\title{\hfill\break
\hfill\break
\vspace{1cm}Writing a reproducible paper\\
in R Markdown\footnote{Corresponding address: \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}. Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
\author{Paul Bauer, Mannheim Centre for European Social Research \and Camille Landesvatter, Mannheim Centre for European Social Research}
\date{\hfill\break
First version: December 14, 2018\\
This version: April 05, 2023\\
Download: \url{https://osf.io/q395s}\\
\strut \\
Feedback? Errors? \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}\\
\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}\\
\strut \\
Tired of Latex?\\
Try \href{https://github.com/rstudio/pagedown}{Pagedown} with our \href{https://osf.io/k8jhx/}{new template}! :-)}

\begin{document}
\maketitle
\begin{abstract}
\noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below we outline some of the ``tricks''/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be downloaded \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{here} (click on Code -\textgreater{} Download ZIP). We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repo}).\vspace{.8cm}
\end{abstract}

@@

\begin{itemize}
\item
  \ldots download the 5 input files we created --- \texttt{paper.rmd}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{Github} (click on Code -\textgreater{} Download ZIP). Ignore the other files.
\item
  \ldots learn R and read about the other underlying components namely \href{https://en.wikipedia.org/wiki/Markdown}{Markdown}, \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
\end{itemize}

@@

\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown}{Download these files from Github} (click on Code -\textgreater{} Download ZIP) and save them into a folder. Close R/Rstudio and directly open \texttt{paper.rmd} with RStudio. Doing so assures that the working directory is set to the folder that contains \texttt{paper.rmd} and the other files.\footnote{You can always check your working directory in R with \texttt{getwd()}.}

@@

In the present document we use the style of the American Sociological Association and set it in the preamble with \texttt{csl:\ american-sociological-association.csl}. However, you also need to download the respective \texttt{.csl} file from the following Github page: \url{https://github.com/citation-style-language/styles} and copy it into your working directory for it to work.

The Github directory contains a wide variety of citation style files depending on what discipline you work in.

@@

\begin{verbatim}
## R version 4.2.2 (2022-10-31)
## Platform: aarch64-apple-darwin20 (64-bit)
## Running under: macOS Ventura 13.0.1
## 
## Matrix products: default
## BLAS:   /Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/lib/libRblas.0.dylib
## LAPACK: /Library/Frameworks/R.framework/Versions/4.2-arm64/Resources/lib/libRlapack.dylib
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] ggplot2_3.4.2    kableExtra_1.3.4 knitr_1.42       stargazer_5.2.3 
## 
## loaded via a namespace (and not attached):
##  [1] compiler_4.2.2    pillar_1.9.0      tools_4.2.2       digest_0.6.31    
##  [5] evaluate_0.20     lifecycle_1.0.3   tibble_3.2.1      gtable_0.3.3     
##  [9] viridisLite_0.4.1 pkgconfig_2.0.3   rlang_1.1.0       cli_3.6.1        
## [13] rstudioapi_0.14   yaml_2.3.7        xfun_0.38         fastmap_1.1.1    
## [17] withr_2.5.0       dplyr_1.1.1       httr_1.4.5        stringr_1.5.0    
## [21] xml2_1.3.3        generics_0.1.3    vctrs_0.6.1       systemfonts_1.0.4
## [25] tidyselect_1.2.0  webshot_0.5.4     grid_4.2.2        svglite_2.1.1    
## [29] glue_1.6.2        R6_2.5.1          fansi_1.0.4       rmarkdown_2.21   
## [33] bookdown_0.33     farver_2.1.1      magrittr_2.0.3    scales_1.2.1     
## [37] htmltools_0.5.5   rvest_1.0.3       colorspace_2.1-0  labeling_0.4.2   
## [41] utf8_1.2.3        stringi_1.7.12    munsell_0.5.0
\end{verbatim}
